Risk Perceptions for Wearable Devices

### 2015-03-04 tex-inputs/results-type.tex
Added reference

\subsubsection{Data Type}
Based on our data, we observed that the largest effect stemmed from the data being shared. We present various statistical models in section \ref{sec:regression} to support this conclusion. The 10 top and bottom concerning data can be seen in Table \ref{top10-table}, and the full list of data can be seen in Appendix [?].

@@

The data types examined span several existing and future use cases. We do not believe they are comprehensive in coverage of how wearable devices might capture data nor for all possible future use cases of the data. Therefore, we coded each data type in two ways: firstly in terms in the data and how it was captured (e.g., video, audio, text, etc.), and  secondly in terms of the type of risks presented to the user. This examines why participants viewed certain data collected as more/less risky than others, letting us  generalize our results. Two researchers agreed on a codebook and independently coded each of the 72 data types\footnote{We excluded the data types that did not feature a data recipient.}.

>>>>

\subsubsection{Data Type}
\label{sec:datatypes}

Based on our data, we observed that the largest effect stemmed from the data being shared. We present various statistical models in section \ref{sec:regression} to support this conclusion. The 10 top and bottom concerning data can be seen in Table \ref{top10-table}, and the full list of data can be seen in Appendix [?].

@@

The data types examined span several existing and future use cases. We do not believe they are comprehensive in coverage of how wearable devices might capture data nor for all possible future use cases of the data. Therefore, we coded each data type in two ways: firstly in terms in the data and how it was captured (e.g., video, audio, text, etc.), and  secondly in terms of the type of risks presented to the user. This examines why participants viewed certain data collected as more/less risky than others, letting us  generalize our results. Two researchers agreed on a codebook and independently coded each of the 72 data types.\footnote{We excluded the data types that did not feature a data recipient, the five misbehaviors used to examine device types.}
